### 2024-06-24 basic-statistics.qmd
20240624 - balanced vs unbalanced group sizes

@@

>>>>

##### Balanced Group Sizes {#sec-statisticalPowerIndependentSamplesTtestBalanced}

@@

##### Unbalanced Group Sizes {#sec-statisticalPowerIndependentSamplesTtestUnbalanced}

```{r}
pwr::pwr.t2n.test(
  n1 = nGroup1,
  n2 = nGroup2,
  d = effectSize_d,
  sig.level = alpha,
  alternative = "two.sided")
```

```{r}
pwr::pwr.t2n.test(
  n1 = nGroup1,
  d = effectSize_d,
  power = power,
  sig.level = alpha,
  alternative = "two.sided")
```

```{r}
pwr::pwr.t2n.test(
  n1 = nGroup1,
  n2 = nGroup2,
  power = power,
  sig.level = alpha,
  alternative = "two.sided")
```
